What do they see? Testing perceptual accuracy in a U.S. general population survey using stacked bar charts

### 2023-10-25 SDSS-2023/testing-charts-accuracy.qmd
updated income table

acs_income <- data.frame(
  income4 = c("< $30k", "$30k - $60k", 
              "$60k - $100k", "more than $100k"), 
  percent = c(6+3.9+7.5+ .5*7.8, 
              .5*7.8 + 11.3 + .4*16.8, 
              .6*16.8+12.8,
              16.3+7.9+9.8),
  moe_percent = c(sqrt(0.1^2+0.1^2+0.1^2+0.1^2+0.1^2),
                  sqrt(0.1^2+0.1^2+0.1^2),
                  sqrt(0.1^2 + 0.1^2),
                  sqrt(0.1^2+0.1^2+0.1^2))
  )

# Household income
# Less than $10,000	6.0
# $10,000 to $14,999	3.9
# $15,000 to $24,999	7.5
# $25,000 to $34,999	7.8
# $35,000 to $49,999	11.3
# $50,000 to $74,999	16.8
# $75,000 to $99,999	12.8
# $100,000 to $149,999	16.3
# $150,000 to $199,999	7.9
# $200,000 or more	9.8

# 
# acs_income <- data.frame(
#   income4 = c("< $30k", "$30k - $60k", 
#               "$60k - $100k", "more than $100k"), 
#   percent = c(1807928 + 2669815 + 10192511 + .5*16440260, 
#               .5*16440260+ 21573641+ 2/3*17579780, 
#               1/3*17579780 + 8347923+13881892, 
#               21161141)/113654891*100 )
# Population age 18 and over
# FULL-TIME, YEAR-ROUND WORKERS WITH EARNINGS	113654891	79395	
# $1 to $9,999 or loss	1807928	11027	1.6	0.1
# $10,000 to $14,999	2669815	16330	2.3	0.1
# $15,000 to $24,999	10192511	50628	9.0	0.1
# $25,000 to $34,999	16440260	63750	14.5	0.1
# $35,000 to $49,999	21573641	44746	19.0	0.1
# $50,000 to $64,999	17579780	35183	15.5	0.1
# $65,000 to $74,999	8347923	32204	7.3	0.1
# $75,000 to $99,999	13881892	50191	12.2	0.1
# $100,000 or more	21161141	100258	18.6	0.1

>>>>

acs_income_raw <- read_xlsx("../data/ACSDT1Y2021.B19001-income.xlsx", sheet="Data", skip = 1) %>% mutate(
  estimate = parse_number(Estimate), 
  moe = parse_number(`Margin of Error`)
)
acs_income_raw <- acs_income_raw %>% mutate(
  income4 = c("Total", rep("< $30k", 5), rep("$30k - $60k", 5), rep("$60k - $100k", 2), rep("more than $100k", 4))
)

acs_income2 <- acs_income_raw %>% group_by(income4) %>% 
  summarize(
    moe = tidycensus::moe_sum(moe, estimate),
    estimate = sum(estimate)
  )
acs_income2 <- acs_income2 %>% mutate(
  percent = estimate/estimate[income4=="Total"]*100,
  moe_percent = moe_prop(estimate, rep(estimate[income4=="Total"], n()), 
                      100*moe, 100*rep(moe[income4=="Total"], n()))
)
acs_income <- acs_income2 %>%
  filter(income4 != "Total") %>%
  mutate(
  income4 = factor(income4, levels = c("< $30k", "$30k - $60k", 
              "$60k - $100k", "more than $100k"))
)
